Adaptive broadcast tree for multicores

### 2013-06-04 graphs/visu_gruyere_sequential.tex
Added forgotten file

\node at (0mm,480mm) {Machine: gruyere, topology: mst};
\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (60mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (70mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (80mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (70mm,60mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_4_8) at (80mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_20) at (90mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (100mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (110mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (120mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (80mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (90mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (100mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (110mm,240mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (91mm,30mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_8) at (100mm,120mm) {};
\draw[->,very thick,color=red] (s_4_8.center) -- (r_4_8.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_8_28) at (110mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (120mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (130mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (140mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (150mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (160mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (101mm,285mm) {};
\draw[->] (s_16_19.center) -- (r_16_19.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_4_20) at (110mm,300mm) {};
\draw[->,very thick,color=red] (s_4_20.center) -- (r_4_20.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (120mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (130mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (140mm,300mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (111mm,105mm) {};
\draw[->] (s_4_7.center) -- (r_4_7.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (111mm,270mm) {};
\draw[->] (s_16_18.center) -- (r_16_18.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (121mm,255mm) {};
\draw[->] (s_16_17.center) -- (r_16_17.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (121mm,90mm) {};
\draw[->] (s_4_6.center) -- (r_4_6.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_28) at (130mm,420mm) {};
\draw[->,very thick,color=red] (s_8_28.center) -- (r_8_28.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (140mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (150mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (160mm,420mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (131mm,345mm) {};
\draw[->] (s_20_23.center) -- (r_20_23.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (131mm,75mm) {};
\draw[->] (s_4_5.center) -- (r_4_5.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (140mm,360mm) {};
\draw[->,very thick,color=red] (s_8_24.center) -- (r_8_24.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (150mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (160mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (170mm,360mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (141mm,330mm) {};
\draw[->] (s_20_22.center) -- (r_20_22.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (150mm,180mm) {};
\draw[->,very thick,color=red] (s_8_12.center) -- (r_8_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (160mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (170mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (180mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (151mm,165mm) {};
\draw[->] (s_8_11.center) -- (r_8_11.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (151mm,465mm) {};
\draw[->] (s_28_31.center) -- (r_28_31.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (151mm,315mm) {};
\draw[->] (s_20_21.center) -- (r_20_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (161mm,450mm) {};
\draw[->] (s_28_30.center) -- (r_28_30.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (161mm,405mm) {};
\draw[->] (s_24_27.center) -- (r_24_27.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (161mm,150mm) {};
\draw[->] (s_8_10.center) -- (r_8_10.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (171mm,225mm) {};
\draw[->] (s_12_15.center) -- (r_12_15.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (171mm,390mm) {};
\draw[->] (s_24_26.center) -- (r_24_26.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (171mm,435mm) {};
\draw[->] (s_28_29.center) -- (r_28_29.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (171mm,135mm) {};
\draw[->] (s_8_9.center) -- (r_8_9.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (181mm,210mm) {};
\draw[->] (s_12_14.center) -- (r_12_14.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (181mm,375mm) {};
\draw[->] (s_24_25.center) -- (r_24_25.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (191mm,195mm) {};
\draw[->] (s_12_13.center) -- (r_12_13.center);

>>>>

\node at (0mm,480mm) {Machine: gruyere, topology: sequential};
\node[draw,fill=red!20,minimum size=10mm] (s_0_31) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_30) at (60mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_29) at (70mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_28) at (80mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_27) at (90mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_26) at (100mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_25) at (110mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_24) at (120mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_15) at (130mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_14) at (140mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_13) at (150mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_12) at (160mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_23) at (170mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_22) at (180mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_21) at (190mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_20) at (200mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_11) at (210mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_10) at (220mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_9) at (230mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (240mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_19) at (250mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_18) at (260mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_17) at (270mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (280mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_7) at (290mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_6) at (300mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_5) at (310mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (320mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (330mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (340mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (350mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_31) at (90mm,465mm) {};
\draw[->,very thick,color=red] (s_0_31.center) -- (r_0_31.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_30) at (100mm,450mm) {};
\draw[->,very thick,color=red] (s_0_30.center) -- (r_0_30.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_29) at (110mm,435mm) {};
\draw[->,very thick,color=red] (s_0_29.center) -- (r_0_29.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_28) at (120mm,420mm) {};
\draw[->,very thick,color=red] (s_0_28.center) -- (r_0_28.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_27) at (130mm,405mm) {};
\draw[->,very thick,color=red] (s_0_27.center) -- (r_0_27.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_26) at (140mm,390mm) {};
\draw[->,very thick,color=red] (s_0_26.center) -- (r_0_26.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_25) at (150mm,375mm) {};
\draw[->,very thick,color=red] (s_0_25.center) -- (r_0_25.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_24) at (160mm,360mm) {};
\draw[->,very thick,color=red] (s_0_24.center) -- (r_0_24.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_15) at (170mm,225mm) {};
\draw[->,very thick,color=red] (s_0_15.center) -- (r_0_15.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_14) at (180mm,210mm) {};
\draw[->,very thick,color=red] (s_0_14.center) -- (r_0_14.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_13) at (190mm,195mm) {};
\draw[->,very thick,color=red] (s_0_13.center) -- (r_0_13.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_23) at (200mm,345mm) {};
\draw[->,very thick,color=red] (s_0_23.center) -- (r_0_23.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_12) at (200mm,180mm) {};
\draw[->,very thick,color=red] (s_0_12.center) -- (r_0_12.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_22) at (210mm,330mm) {};
\draw[->,very thick,color=red] (s_0_22.center) -- (r_0_22.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_21) at (220mm,315mm) {};
\draw[->,very thick,color=red] (s_0_21.center) -- (r_0_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_20) at (230mm,300mm) {};
\draw[->,very thick,color=red] (s_0_20.center) -- (r_0_20.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_11) at (240mm,165mm) {};
\draw[->,very thick,color=red] (s_0_11.center) -- (r_0_11.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_10) at (250mm,150mm) {};
\draw[->,very thick,color=red] (s_0_10.center) -- (r_0_10.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_9) at (260mm,135mm) {};
\draw[->,very thick,color=red] (s_0_9.center) -- (r_0_9.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (270mm,120mm) {};
\draw[->,very thick,color=red] (s_0_8.center) -- (r_0_8.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_19) at (270mm,285mm) {};
\draw[->,very thick,color=red] (s_0_19.center) -- (r_0_19.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_18) at (280mm,270mm) {};
\draw[->,very thick,color=red] (s_0_18.center) -- (r_0_18.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_17) at (290mm,255mm) {};
\draw[->,very thick,color=red] (s_0_17.center) -- (r_0_17.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (300mm,240mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_7) at (310mm,105mm) {};
\draw[->,very thick,color=red] (s_0_7.center) -- (r_0_7.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_6) at (320mm,90mm) {};
\draw[->,very thick,color=red] (s_0_6.center) -- (r_0_6.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_5) at (330mm,75mm) {};
\draw[->,very thick,color=red] (s_0_5.center) -- (r_0_5.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (340mm,60mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (341mm,45mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (351mm,30mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (361mm,15mm) {};

@@

### 2013-06-04 graphs/visu_sbrinz_badtree.tex
Added forgotten file

\draw[fill,color=red!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
\node at (0mm,240mm) {core 16};
\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
\draw[fill,color=red!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
\node at (0mm,255mm) {core 17};
\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
\draw[fill,color=red!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
\node at (0mm,270mm) {core 18};
\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
\draw[fill,color=red!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
\node at (0mm,285mm) {core 19};
\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
\draw[fill,color=green!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
\node at (0mm,300mm) {core 20};
\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
\draw[fill,color=green!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
\node at (0mm,315mm) {core 21};
\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
\draw[fill,color=green!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
\node at (0mm,330mm) {core 22};
\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
\draw[fill,color=green!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
\node at (0mm,345mm) {core 23};
\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
\draw[fill,color=blue!10] (-3cm,367.500000mm) rectangle (30cm,352.500000mm);
\node at (0mm,360mm) {core 24};
\draw[color=black!30] (20mm,360mm) -- (30cm,360mm);
\draw[fill,color=blue!10] (-3cm,382.500000mm) rectangle (30cm,367.500000mm);
\node at (0mm,375mm) {core 25};
\draw[color=black!30] (20mm,375mm) -- (30cm,375mm);
\draw[fill,color=blue!10] (-3cm,397.500000mm) rectangle (30cm,382.500000mm);
\node at (0mm,390mm) {core 26};
\draw[color=black!30] (20mm,390mm) -- (30cm,390mm);
\draw[fill,color=blue!10] (-3cm,412.500000mm) rectangle (30cm,397.500000mm);
\node at (0mm,405mm) {core 27};
\draw[color=black!30] (20mm,405mm) -- (30cm,405mm);
\draw[fill,color=orange!10] (-3cm,427.500000mm) rectangle (30cm,412.500000mm);
\node at (0mm,420mm) {core 28};
\draw[color=black!30] (20mm,420mm) -- (30cm,420mm);
\draw[fill,color=orange!10] (-3cm,442.500000mm) rectangle (30cm,427.500000mm);
\node at (0mm,435mm) {core 29};
\draw[color=black!30] (20mm,435mm) -- (30cm,435mm);
\draw[fill,color=orange!10] (-3cm,457.500000mm) rectangle (30cm,442.500000mm);
\node at (0mm,450mm) {core 30};
\draw[color=black!30] (20mm,450mm) -- (30cm,450mm);
\draw[fill,color=orange!10] (-3cm,472.500000mm) rectangle (30cm,457.500000mm);
\node at (0mm,465mm) {core 31};
\draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
\node at (0mm,480mm) {Machine: gruyere, topology: binarytree};
\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (60mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (61mm,15mm) {};
\draw[->] (s_0_1.center) -- (r_0_1.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_1_3) at (71mm,15mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_1_4) at (81mm,15mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (71mm,30mm) {};
\draw[->] (s_0_2.center) -- (r_0_2.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_2_6) at (81mm,30mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_2_5) at (91mm,30mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_1_3) at (82mm,45mm) {};
\draw[->] (s_1_3.center) -- (r_1_3.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (92mm,45mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_3_7) at (102mm,45mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_1_4) at (101mm,60mm) {};
\draw[->,very thick,color=red] (s_1_4.center) -- (r_1_4.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_4_9) at (111mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_10) at (121mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_2_6) at (101mm,90mm) {};
\draw[->,very thick,color=red] (s_2_6.center) -- (r_2_6.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_6_14) at (111mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_13) at (121mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_2_5) at (111mm,75mm) {};
\draw[->,very thick,color=red] (s_2_5.center) -- (r_2_5.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_5_12) at (121mm,75mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_5_11) at (131mm,75mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_3_7) at (122mm,105mm) {};
\draw[->,very thick,color=red] (s_3_7.center) -- (r_3_7.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (132mm,105mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_7_16) at (142mm,105mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (122mm,120mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_8_18) at (132mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_17) at (142mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_9) at (131mm,135mm) {};
\draw[->,very thick,color=red] (s_4_9.center) -- (r_4_9.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_9_19) at (141mm,135mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_9_20) at (151mm,135mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_6_14) at (141mm,210mm) {};
\draw[->,very thick,color=red] (s_6_14.center) -- (r_6_14.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_14_30) at (151mm,210mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_14_29) at (161mm,210mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_10) at (141mm,150mm) {};
\draw[->,very thick,color=red] (s_4_10.center) -- (r_4_10.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_10_22) at (151mm,150mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_10_21) at (161mm,150mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_6_13) at (151mm,195mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_13_28) at (161mm,195mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_13_27) at (171mm,195mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_5_11) at (151mm,165mm) {};
\draw[->,very thick,color=red] (s_5_11.center) -- (r_5_11.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_11_23) at (161mm,165mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_11_24) at (171mm,165mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_5_12) at (151mm,180mm) {};
\draw[->,very thick,color=red] (s_5_12.center) -- (r_5_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_26) at (161mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_25) at (171mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (162mm,225mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_15_31) at (172mm,225mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_14_30) at (171mm,450mm) {};
\draw[->,very thick,color=red] (s_14_30.center) -- (r_14_30.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_7_16) at (172mm,240mm) {};
\draw[->,very thick,color=red] (s_7_16.center) -- (r_7_16.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_18) at (172mm,270mm) {};
\draw[->,very thick,color=red] (s_8_18.center) -- (r_8_18.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_9_19) at (181mm,285mm) {};
\draw[->,very thick,color=red] (s_9_19.center) -- (r_9_19.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_9_20) at (181mm,300mm) {};
\draw[->,very thick,color=red] (s_9_20.center) -- (r_9_20.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_13_28) at (181mm,420mm) {};
\draw[->,very thick,color=red] (s_13_28.center) -- (r_13_28.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_10_22) at (181mm,330mm) {};
\draw[->,very thick,color=red] (s_10_22.center) -- (r_10_22.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_26) at (181mm,390mm) {};
\draw[->,very thick,color=red] (s_12_26.center) -- (r_12_26.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_14_29) at (181mm,435mm) {};
\draw[->,very thick,color=red] (s_14_29.center) -- (r_14_29.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_17) at (182mm,255mm) {};
\draw[->,very thick,color=red] (s_8_17.center) -- (r_8_17.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_13_27) at (191mm,405mm) {};
\draw[->,very thick,color=red] (s_13_27.center) -- (r_13_27.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_25) at (191mm,375mm) {};
\draw[->,very thick,color=red] (s_12_25.center) -- (r_12_25.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_11_24) at (191mm,360mm) {};
\draw[->,very thick,color=red] (s_11_24.center) -- (r_11_24.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_11_23) at (191mm,345mm) {};
\draw[->,very thick,color=red] (s_11_23.center) -- (r_11_23.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_10_21) at (191mm,315mm) {};
\draw[->,very thick,color=red] (s_10_21.center) -- (r_10_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_15_31) at (192mm,465mm) {};
\draw[->,very thick,color=red] (s_15_31.center) -- (r_15_31.center);

>>>>

\node at (0mm,240mm) {Machine: sbrinz, topology: badtree};
\node[draw,fill=red!20,minimum size=10mm] (s_0_9) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_10) at (60mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_9) at (80mm,135mm) {};
\draw[->,very thick,color=red] (s_0_9.center) -- (r_0_9.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_9_6) at (90mm,135mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_9_2) at (100mm,135mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_10) at (90mm,150mm) {};
\draw[->,very thick,color=red] (s_0_10.center) -- (r_0_10.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_10_3) at (100mm,150mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_10_1) at (110mm,150mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_9_6) at (110mm,90mm) {};
\draw[->,very thick,color=red] (s_9_6.center) -- (r_9_6.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_6_12) at (120mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_13) at (130mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_10_3) at (130mm,45mm) {};
\draw[->,very thick,color=red] (s_10_3.center) -- (r_10_3.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_3_11) at (140mm,45mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (150mm,45mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_9_2) at (130mm,30mm) {};
\draw[->,very thick,color=red] (s_9_2.center) -- (r_9_2.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_10_1) at (140mm,15mm) {};
\draw[->,very thick,color=red] (s_10_1.center) -- (r_10_1.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_6_12) at (150mm,180mm) {};
\draw[->,very thick,color=red] (s_6_12.center) -- (r_6_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_7) at (160mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_4) at (170mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_6_13) at (160mm,195mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_13_5) at (170mm,195mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_3_11) at (170mm,165mm) {};
\draw[->,very thick,color=red] (s_3_11.center) -- (r_3_11.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (180mm,120mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_12_7) at (190mm,105mm) {};
\draw[->,very thick,color=red] (s_12_7.center) -- (r_12_7.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (200mm,105mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_7_14) at (210mm,105mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_13_5) at (200mm,75mm) {};
\draw[->,very thick,color=red] (s_13_5.center) -- (r_13_5.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_4) at (200mm,60mm) {};
\draw[->,very thick,color=red] (s_12_4.center) -- (r_12_4.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (230mm,225mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_7_14) at (240mm,210mm) {};
\draw[->,very thick,color=red] (s_7_14.center) -- (r_7_14.center);
